Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-11-01 paper/lncsFormat.tex
the table about extraction effects is done

%TODO 这个table需要增加BTM生成的和aviation最相近的一个topic的情况。
\hlgreen{TODO: add a new table, containing a topic generated by BTM, which is most similar to the extracted topic from KB.}
\begin{table}[]
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Top words' topic coherence of \textit{Aviation}'s history state. * means the group also contains the five top words \textit{aircraft}, \textit{air}, \textit{airport}, \textit{flight}, and \textit{airline}, but we don't show them in table to save space. NPMI is computed on ten words (a combination of words in each row with the five top words).}
\scalebox{0.76}{
\begin{tabular}{|c|l|l|l !{\vrule width 1pt} c|l|l|l|}
\hline
\multicolumn{4}{|c!{\vrule width 1pt}}{TransDetector} & \multicolumn{4}{c|}{LightLDA}    \\ \hline
\#group*  & \#words*  & words  & NPMI & \#group* & \#words* & words & NPMI \\ \hline
0 & 6-10 & airlines aviation flying pilot squadron &  0.113 & 0 & 6-10 & & \\ \hline
1 & 11-15 &flights pilots raf airways fighter & 0.155 & 1 & 11-15 & & \\ \hline
2 & 16-20 &boeing runway force crashed flew   & 0.092 & 2 & 16-20 & & \\ \hline
3 & 21-25 &airfield landing passengers plane aerial & 0.179 & 3 & 21-25 & & \\ \hline
4 & 26-30 &bomber radar wing bombers crash & 0.137 & 4 & 26-30 & & \\ \hline
5 & 31-35 &airbus airports operations jet helicopter & 0.189 & 5 & 31-35 & & \\ \hline
6 & 36-40 &squadrons base flown havilland crew & 0.088 & 6 & 36-40 & & \\ \hline
7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 41-45 & & \\ \hline
8 & 46-50 &planes fly engine takeoff fleet & 0.186 & 8 & 46-50 & & \\ \hline
9 & 51-55 &fuselage helicopters aviator naval aero & 0.157 & 9 & 51-55 & & \\ \hline
10 & 56-60 &glider command training balloon faa & 0.166 & 10 & 56-60 & & \\ \hline
\(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\) & \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
18 & 96-100 &scheduled carriers military curtiss biplane &0.131 & 11 & 96-100 & & \\ \hline
19 & 101-105 &accident engines iaf albatross rcaf &0.068 & 12 & 101-105 & & \\ \hline
\end{tabular}
}
\label{tbl:NPMIDetails}
\end{table}

>>>>

%TODO 这个table需要增加BTM生成的和aviation最相近的一个topic的情况。
%\hlgreen{TODO: add a new table, containing a topic generated by BTM, which is most similar to the extracted topic from KB.}
\begin{table}[]
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Top words' topic coherence of \textit{Aviation}'s history state. * means the group also contains the five top words \textit{aircraft}, \textit{air}, \textit{airport}, \textit{flight}, and \textit{airline}, but we don't show them in table to save space. NPMI is computed on ten words (a combination of words in each row with the five top words).}
\scalebox{0.67}{
\begin{tabular}{|c|l|l|l !{\vrule width 1pt} c|l|l|l|}
\hline
\multicolumn{4}{|c!{\vrule width 1pt}}{TransDetector} & \multicolumn{4}{c|}{LightLDA}    \\ \hline
\#group*  & \#words*  & words  & NPMI & \#group* & \#words* & words & NPMI \\ \hline
-1 & 1-5 & aircraft air airport flight airline &  & -1 & 1-5 & engine aircraft car air power & \\ \hline
0 & 6-10 & airlines aviation flying pilot squadron &  0.113 & 0 & 6-10 & design flight model production speed & 0.112\\ \hline
1 & 11-15 &flights pilots raf airways fighter & 0.155 & 1 & 11-15 &system vehicle cars engines mm & 0.062\\ \hline
2 & 16-20 &boeing runway force crashed flew   & 0.092 & 2 & 16-20 & fuel vehicles designed models type & 0.072\\ \hline
3 & 21-25 &airfield landing passengers plane aerial & 0.179 & 3 & 21-25 & version front produced rear electric & 0.035\\ \hline
4 & 26-30 &bomber radar wing bombers crash & 0.137 & 4 & 26-30 & space control motor standard development & 0.085\\ \hline
5 & 31-35 &airbus airports operations jet helicopter & 0.189 & 5 & 31-35 & film range light using available & -0.002\\ \hline
6 & 36-40 &squadrons base flown havilland crew & 0.088 & 6 & 36-40 & wing powered wheel weight launch & 0.087\\ \hline
7 & 41-45 &combat luftwaffe aerodrome carrier fokker & 0.159 & 7 & 41-45 & developed low test ford cylinder & 0.007\\ \hline
8 & 46-50 &planes fly engine takeoff fleet & 0.186 & 8 & 46-50 & equipment side pilot hp aviation & 0.091\\ \hline
9 & 51-55 &fuselage helicopters aviator naval aero & 0.157 & 9 & 51-55 & systems us sold body drive & -0.051\\ \hline
10 & 56-60 &glider command training balloon faa & 0.166 & 10 & 56-60 & gear introduced class safety seat & 0.069\\ \hline
\(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\) & \(\cdots\) & \(\cdots\) &\(\cdots\) &\(\cdots\)\\ \hline
18 & 96-100 &scheduled carriers military curtiss biplane &0.131 & 18 & 96-100 & transmission special replaced limited different & 0.059\\ \hline
19 & 101-105 &accident engines iaf albatross rcaf &0.068 & 19 & 101-105 & features machine nuclear even unit & 0.011\\ \hline
\end{tabular}
}
\label{tbl:NPMIDetails}
\end{table}
